Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-15 paper/sections/proof-reconstruction.tex
[ paper ] remove use of \tt.

\change{remove the use of tt for functions. (rank, etc..)}
\begin{equation}
\label{eq:unshunt-rank-definition}
\unshunt_{cm}(φ)=
\begin{cases}
\unshunt_{cm}(φ₃) + 2 & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
\max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1
  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
0 &\text{otherwise.}
\end{cases}
\end{equation}

@@

\begin{equation}
\label{eq:unshunt-fixed}
\unshunt(\varphi) := \unshunt_{1}(\varphi, \unshunt_{cm}(\varphi)).
\end{equation}
\change{changes the name of the functions to avoid different
functions with the same name.}

@@

\begin{proof} Use induction on the cases defined by the result of
$\unshunt$ in Eq.~\ref{eq:unshunt-structured}.
When $n = 0$, by definition, $Γ ⊢ φ$.
When $n = 1$, we apply the following theorem presented in
\cite{AgdaProp}

@@

(φ₁ ⇒ (φ₂ ⇒ φ₃))
\begin{equation*}
\begin{bprooftree}
\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
\RightLabel{\tt thm-$\unshunt$}
\UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
\RightLabel{\tt ∧⇒-to-⇒⇒}
\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).}
\end{bprooftree}
\end{equation*}

Second, using the following theorem from \cite{AgdaProp},
\begin{equation*}
\texttt{⇒∧-to-⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).
\end{equation*}

(φ₁ ⇒ (φ₂ ∧ φ₃))
\begin{equation*}
\scalebox{0.95}{
($\mathcal{D}_1$)
\begin{bprooftree}
\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n) ∧ \unshunt(φ₁ ⇒ φ₃, n)$}
\RightLabel{\tt ∧-proj₁}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n-1)$}
\RightLabel{\tt thm-$\unshunt$}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$,}
\end{bprooftree}
}
\end{equation*}

\begin{equation*}
(\mathcal{D}_2)
\begin{bprooftree}
\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂) ∧ \unshunt(φ₁ ⇒ φ₃)$}
\RightLabel{\tt ∧-proj₂}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₃, n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₃, n-1)$}
\RightLabel{\tt thm-$\unshunt$}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$,}
\end{bprooftree}
\end{equation*}

\begin{equation*}
\begin{bprooftree}
\AxiomC{$\mathcal{D}_1$}
\AxiomC{$\mathcal{D}_2$}
\RightLabel{\tt ∧-intro}
\BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
\RightLabel{\tt ⇒∧⇒-to-⇒∧}
\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).}
\end{bprooftree}
\end{equation*}
\end{proof}

@@

\AxiomC{$Γ ⊢ \mysplit(φ,n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{\tt $∧$-proj$₂$}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
\RightLabel{\tt $⇒$-elim}
\BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
\RightLabel{\thmsplit}
\UnaryInfC{$Γ ⊢ φ₂$}

\RightLabel{\tt ∧-intro}
\BinaryInfC{$Γ ⊢ φ₁ ∧ φ₂$.}
\end{bprooftree}
\end{equation*}
Where,
\begin{equation*}
(\mathcal{D}_1)\hspace{3mm}
\begin{bprooftree}
\AxiomC{$Γ ⊢ \mysplit(φ,n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{\tt ∧-proj₁}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁)$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ φ₁$.}
\end{bprooftree}
\end{equation*}

(φ ≡ φ₁ ⇒ φ₂)
\begin{equation*}
\begin{bprooftree}
\AxiomC{}
\RightLabel{\tt assume φ₁}
\UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
\AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
\RightLabel{weaken φ₁}
\UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
\RightLabel{\tt ⇒-elim}
\BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂,n-1)$}
\RightLabel{\thmsplit}
\UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
\RightLabel{\tt ⇒-intro}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$.}
\end{bprooftree}
\end{equation*}

@@

\AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{\tt ∧-proj₂}
\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂,n-1)$}
\RightLabel{\tt ⇒-elim}
\BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
\RightLabel{\thmsplit}
\UnaryInfC{$Γ ⊢ ¬ φ₂$}
\RightLabel{\tt ∧-intro}
\BinaryInfC{$Γ ⊢ ¬ φ₁ ∧ ¬ φ₂$}
\RightLabel{\tt ¬∧¬-to-¬∨}
\UnaryInfC{$Γ ⊢ ¬ (φ₁ ∨ φ₂)$.}
\end{bprooftree}
\end{equation*}

@@

\begin{equation*}
(\mathcal{D})
\begin{bprooftree}
\AxiomC{$Γ ⊢ \mysplit(φ, n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
\RightLabel{\tt ∧-proj₁}
\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁)$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ ¬ φ₁$.}
\end{bprooftree}
\end{equation*}
\end{proof}

@@

\begin{proof}
\begin{equation*}
\begin{bprooftree}
\AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i}$}
\RightLabel{\tt ∧-intro}
\UnaryInfC{$Γ ⊢ \bigwedge_i s_i$}

\AxiomC{$\mysplit(φ) ≡ \bigwedge_i s_i $}
\RightLabel{\tt subst}
\BinaryInfC{$Γ ⊢ \mysplit(φ) $}

\RightLabel{\thmsplit}
\UnaryInfC{$Γ ⊢ φ$.}
\end{bprooftree}
\end{equation*}
Where,
\begin{equation*}
\begin{bprooftree}
\AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
\RightLabel{\tt subst}
\BinaryInfC{$Γ ⊢ ψ$.}
\end{bprooftree}
\end{equation*}
\end{proof}

>>>>

\begin{equation}
\label{eq:unshunt-rank-definition}
\unshunt_{cm}(φ)=
\begin{cases}
\unshunt_{cm}(φ₃) + 2 & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
\max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1
  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
0 &\text{otherwise.}
\end{cases}
\end{equation}

@@

\begin{equation}
\label{eq:unshunt-fixed}
\unshunt(\varphi) := \unshunt_{1}(\varphi, \unshunt_{cm}(\varphi)).
\end{equation}

@@

\begin{proof} Use induction on the cases defined by the outcome of the $\unshunt$ function in Eq.~\ref{eq:unshunt-structured}.
When $n = 0$, by definition, $Γ ⊢ φ$.
When $n = 1$, we apply the following theorem presented in
\cite{AgdaProp}

@@

(φ₁ ⇒ (φ₂ ⇒ φ₃))
\begin{equation*}
\begin{bprooftree}
\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
\RightLabel{\thmunshunt}
\UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
\RightLabel{∧⇒-to-⇒⇒}
\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).}
\end{bprooftree}
\end{equation*}

Second, using the following theorem from \cite{AgdaProp},

\begin{equation*}
\texttt{⇒∧-to-⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).
\end{equation*}

(φ₁ ⇒ (φ₂ ∧ φ₃))
\begin{equation*}
\scalebox{0.95}{
($\mathcal{D}_1$)
\begin{bprooftree}
\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n) ∧ \unshunt(φ₁ ⇒ φ₃, n)$}
\RightLabel{∧-proj₁}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n-1)$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$,}
\end{bprooftree}
}
\end{equation*}

\begin{equation*}
(\mathcal{D}_2)
\begin{bprooftree}
\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂) ∧ \unshunt(φ₁ ⇒ φ₃)$}
\RightLabel{∧-proj₂}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₃, n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₃, n-1)$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$,}
\end{bprooftree}
\end{equation*}

\begin{equation*}
\begin{bprooftree}
\AxiomC{$\mathcal{D}_1$}
\AxiomC{$\mathcal{D}_2$}
\RightLabel{∧-intro}
\BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
\RightLabel{⇒∧⇒-to-⇒∧}
\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).}
\end{bprooftree}
\end{equation*}
\end{proof}

@@

\AxiomC{$Γ ⊢ \mysplit(φ,n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{$∧$-proj$₂$}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
\RightLabel{$⇒$-elim}
\BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
\RightLabel{\thmsplit}
\UnaryInfC{$Γ ⊢ φ₂$}

\RightLabel{∧-intro}
\BinaryInfC{$Γ ⊢ φ₁ ∧ φ₂$.}
\end{bprooftree}
\end{equation*}
Where,
\begin{equation*}
(\mathcal{D}_1)\hspace{3mm}
\begin{bprooftree}
\AxiomC{$Γ ⊢ \mysplit(φ,n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{∧-proj₁}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁)$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ φ₁$.}
\end{bprooftree}
\end{equation*}

(φ ≡ φ₁ ⇒ φ₂)
\begin{equation*}
\begin{bprooftree}
\AxiomC{}
\RightLabel{assume φ₁}
\UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
\AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
\RightLabel{weaken φ₁}
\UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
\RightLabel{⇒-elim}
\BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂,n-1)$}
\RightLabel{\thmsplit}
\UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
\RightLabel{⇒-intro}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$.}
\end{bprooftree}
\end{equation*}

@@

\AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{∧-proj₂}
\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂,n-1)$}
\RightLabel{⇒-elim}
\BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
\RightLabel{\thmsplit}
\UnaryInfC{$Γ ⊢ ¬ φ₂$}
\RightLabel{∧-intro}
\BinaryInfC{$Γ ⊢ ¬ φ₁ ∧ ¬ φ₂$}
\RightLabel{¬∧¬-to-¬∨}
\UnaryInfC{$Γ ⊢ ¬ (φ₁ ∨ φ₂)$.}
\end{bprooftree}
\end{equation*}

@@

\begin{equation*}
(\mathcal{D})
\begin{bprooftree}
\AxiomC{$Γ ⊢ \mysplit(φ, n)$}
\RightLabel{By def.}
\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
\RightLabel{∧-proj₁}
\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁)$}
\RightLabel{\thmunshunt}
\UnaryInfC{$Γ ⊢ ¬ φ₁$.}
\end{bprooftree}
\end{equation*}
\end{proof}

@@

\begin{proof}
\begin{equation*}
\begin{bprooftree}
\AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i}$}
\RightLabel{∧-intro}
\UnaryInfC{$Γ ⊢ \bigwedge_i s_i$}

\AxiomC{$\mysplit(φ) ≡ \bigwedge_i s_i $}
\RightLabel{subst}
\BinaryInfC{$Γ ⊢ \mysplit(φ) $}

\RightLabel{\thmsplit}
\UnaryInfC{$Γ ⊢ φ$.}
\end{bprooftree}
\end{equation*}
Where,
\begin{equation*}
\begin{bprooftree}
\AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
\RightLabel{subst}
\BinaryInfC{$Γ ⊢ ψ$.}
\end{bprooftree}
\end{equation*}
\end{proof}
